Studying measurement invariance in factor analysis models via stochastic processes

### 2011-01-12 MIpaper/par_instable.tex
added to general discussion
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@19 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

Relatedly,
S\'{a}nchez \citeyear{San09} describes a general
method for partitioning/segmenting structural equation models within a 
partial least squares framework.  This method involves direct maximization of
the likelihood ratio (i.e., fitting the model for various subgroups based on
$V$ and choosing the subgroups with the largest likelihood ratio),
however, instead of the tests described in this paper.  The tests
described here are highly advantageous because they only require the
model to be estimated once.
